---
title: "p8105_hw6_as5457"
author: "Sunny Siddique"
date: "November 24, 2018"
output: github_document
---

#Problem 1

Create a city_state variable (e.g. “Baltimore, MD”), and a binary variable indicating whether the homicide is solved. Omit cities Dallas, TX; Phoenix, AZ; and Kansas City, MO – these don’t report victim race. Also omit Tulsa, AL – this is a data entry mistake. Modifiy victim_race to have categories white and non-white, with white as the reference category. Be sure that  victim_age is numeric.

```{r}
library(tidyverse)
homicide_data = read_csv("./homicide-data.csv") %>% 
  janitor::clean_names()
```

```{r}
homicide_clean = homicide_data %>% 
  mutate(city_state = str_c(city, state, sep = ", "),
         solved = as.numeric (disposition == "Closed by arrest")) %>% 
  filter(!city_state %in% c("Dallas, TX","Phoenix, AZ", "Kansas City, MO", "Tulsa, AL")) %>% 
  mutate (victim_race = recode(victim_race, "White" = "white", "Hispanic" = "non-white", "Other" = "non-white", "Black" = "non-white", "Asian" = "non-white")) %>% 
  mutate(victim_race = fct_relevel(victim_race, "white")) %>% 
  mutate(victim_age = as.numeric(victim_age))
```


```{r}
class(homicide_clean$victim_age)
```

For the city of Baltimore, MD, use the glm function to fit a logistic regression with resolved vs unresolved as the outcome and victim age, sex and race (as just defined) as predictors. Save the output of glm as an R object; apply the broom::tidy to this object; and obtain the estimate and confidence interval of the adjusted odds ratio for solving homicides comparing non-white victims to white victims keeping all other variables fixed.


```{r}
baltimore_logistic = homicide_clean %>% 
  filter(city_state == "Baltimore, MD") %>% 
  glm(solved ~ victim_age + victim_sex + victim_race, data = ., family = binomial())
baltimore_logistic
```

```{r}
baltimore_logistic %>% 
  broom::tidy() %>% 
  mutate(OR = exp(estimate),
         lower_bound = exp(estimate - std.error*1.96), upper_bound = exp(estimate + std.error*1.96))
```

The odds of a non-white person's case being solved is 0.441 times the odds of a white person's case being solved. We are 95% confident that the true odds ratio falls between 0.313 and 0.620.

Now run glm for each of the cities in your dataset, and extract the adjusted odds ratio (and CI) for solving homicides comparing non-white victims to white victims. Do this within a “tidy” pipeline, making use of purrr::map, list columns, and unnest as necessary to create a dataframe with estimated ORs and CIs for each city.


```{r}
all_cities = homicide_clean %>% 
  group_by(city_state) %>% 
  nest() %>% 
  mutate(cities = map(data, ~glm(solved ~ victim_age + victim_sex + victim_race, data = .x, family = binomial())),
    cities = map(cities, broom::tidy)) %>% 
   select(-data) %>% 
  unnest() %>% 
  filter(term == "victim_racenon-white") %>% 
  mutate(OR = exp(estimate),
         conf_low = exp(estimate - std.error*1.96),
         conf_high = exp(estimate + std.error*1.96)) %>%
  select(city_state, term, log_OR = estimate, OR, conf_low, conf_high, p.value)
all_cities
```


Create a plot that shows the estimated ORs and CIs for each city. Organize cities according to estimated OR, and comment on the plot.

```{r}
all_cities %>% 
  mutate(city_state = fct_reorder(city_state, OR)) %>%
  ggplot(aes(x = city_state, y = OR)) + geom_point() +
  geom_errorbar(mapping = aes(ymin = conf_low, ymax = conf_high)) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  labs (
    title = "Estimated ORs and CIs",
        x = "City",
        y = "Estimate"
  )
```

#COMMENT

##Problem 2

Load and clean the data for regression analysis (i.e. convert numeric to factor where appropriate, check for missing data, etc.).

```{r}
birthweight = read_csv("./birthweight.csv") %>% 
  janitor::clean_names()
```

```{r}
sapply(birthweight, class)
```

Need to convert babysex, malform, frace, mrace from numeric to factor

```{r}
birthweight = birthweight %>% 
  mutate(babysex = as.factor(babysex), 
         malform = as.factor (malform),
         frace = as.factor(frace), 
         mrace = as.factor(mrace))
```

Looking for missing values 

```{r}
sapply(birthweight, function(x) sum(is.na(x)))
```

No missing values in the dataset. 

Propose a regression model for birthweight. This model may be based on a hypothesized structure for the factors that underly birthweight, on a data-driven model-building process, or a combination of the two. Describe your modeling process and show a plot of model residuals against fitted values – use add_predictions and add_residuals in making this plot.


Exploring the relationship between birthweight and mother's weight at delivery.
```{r}
ggplot(birthweight, aes(babysex, delwt)) + geom_boxplot()
```

