---
title: "Data Science I - Homework 6"
author: "Sunny Siddique"
date: "November 24, 2018"
output: github_document
---

#Problem 1

Create a city_state variable (e.g. “Baltimore, MD”), and a binary variable indicating whether the homicide is solved. Omit cities Dallas, TX; Phoenix, AZ; and Kansas City, MO – these don’t report victim race. Also omit Tulsa, AL – this is a data entry mistake. Modifiy victim_race to have categories white and non-white, with white as the reference category. Be sure that  victim_age is numeric.

```{r include = FALSE}
library(tidyverse)
```


```{r}
#Loading the dataset and naming it homicide_data
homicide_data = read_csv("./homicide-data.csv") %>% 
  janitor::clean_names()
```

```{r warning = FALSE}
#Creating city_state variable, binary variable for solved cases, omitting certain cities, modifying victim race and converting victim_age as numeric.
homicide_clean = homicide_data %>% 
  mutate(city_state = str_c(city, state, sep = ", "),
         solved = as.numeric (disposition == "Closed by arrest")) %>% 
  filter(!city_state %in% c("Dallas, TX","Phoenix, AZ", "Kansas City, MO", "Tulsa, AL")) %>% 
  mutate (victim_race = recode(victim_race, "White" = "white", "Hispanic" = "non-white", "Other" = "non-white", "Black" = "non-white", "Asian" = "non-white")) %>% 
  mutate(victim_race = fct_relevel(victim_race, "white")) %>% 
  mutate(victim_age = as.numeric(victim_age))
```


```{r}
#Confirming that victim_age was converted correctly
class(homicide_clean$victim_age)
```

For the city of Baltimore, MD, use the glm function to fit a logistic regression with resolved vs unresolved as the outcome and victim age, sex and race (as just defined) as predictors. Save the output of glm as an R object; apply the broom::tidy to this object; and obtain the estimate and confidence interval of the adjusted odds ratio for solving homicides comparing non-white victims to white victims keeping all other variables fixed.


```{r}
#Creating dataset and regression for "Baltimore"
baltimore_logistic = homicide_clean %>% 
  filter(city_state == "Baltimore, MD") %>% 
  glm(solved ~ victim_age + victim_sex + victim_race, data = ., family = binomial())
baltimore_logistic
```

```{r}
#Computing confidence intervals
baltimore_logistic %>% 
  broom::tidy() %>% 
  mutate(OR = exp(estimate),
         lower_bound = exp(estimate - std.error*1.96), upper_bound = exp(estimate + std.error*1.96))
```

*The odds of a non-white person's case being solved is 0.441 times the odds of a white person's case being solved. We are 95% confident that the true odds ratio falls between 0.313 and 0.620.*

Now run glm for each of the cities in your dataset, and extract the adjusted odds ratio (and CI) for solving homicides comparing non-white victims to white victims. Do this within a “tidy” pipeline, making use of purrr::map, list columns, and unnest as necessary to create a dataframe with estimated ORs and CIs for each city.


```{r}
#GLM for all cities
all_cities = homicide_clean %>% 
  group_by(city_state) %>% 
  nest() %>% 
  mutate(cities = map(data, ~glm(solved ~ victim_age + victim_sex + victim_race, data = .x, family = binomial())),
    cities = map(cities, broom::tidy)) %>% 
   select(-data) %>% 
  unnest() %>% 
  filter(term == "victim_racenon-white") %>% 
  mutate(OR = exp(estimate),
         conf_low = exp(estimate - std.error*1.96),
         conf_high = exp(estimate + std.error*1.96)) %>%
  select(city_state, term, log_OR = estimate, OR, conf_low, conf_high, p.value)
```


Create a plot that shows the estimated ORs and CIs for each city. Organize cities according to estimated OR, and comment on the plot.

```{r}
all_cities %>% 
  mutate(city_state = fct_reorder(city_state, OR)) %>%
  ggplot(aes(x = city_state, y = OR)) + geom_point() +
  geom_errorbar(mapping = aes(ymin = conf_low, ymax = conf_high)) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  labs (
    title = "Estimated ORs and CIs",
        x = "City",
        y = "Estimate"
  )
```

*It appears that in cities like Boston, Omaha, Oakland, Pittsburgh etc. the odds of having the case resolved for a non-white person is statistially significantly lower compared to a white person. For cities on the other end, such as Tampa, Birmingham, Durham the estimate suggests that there is not much disparity in the odds of having the case resolved between a non-white and white person; however, these estimates are not statistically significant at the 5% level of significance, because their 95% confidence interval error bars include the null value of 1.*

#Problem 2

Load and clean the data for regression analysis (i.e. convert numeric to factor where appropriate, check for missing data, etc.).

```{r}
#Loading the dataset
birthweight = read_csv("./birthweight.csv") %>% 
  janitor::clean_names()
```

```{r}
#Checking the class of all variables to identify which ones need to be converted
sapply(birthweight, class)
```

*Need to convert babysex, malform, frace, mrace from numeric to factor.*

```{r}
#Mutating select variables
birthweight = birthweight %>% 
  mutate(babysex = as.factor(babysex), 
         malform = as.factor (malform),
         frace = as.factor(frace), 
         mrace = as.factor(mrace))
```

```{r}
#Looking for missing values 
sapply(birthweight, function(x) sum(is.na(x)))
```

*No missing values in the dataset.*

Propose a regression model for birthweight. This model may be based on a hypothesized structure for the factors that underly birthweight, on a data-driven model-building process, or a combination of the two. Describe your modeling process and show a plot of model residuals against fitted values – use add_predictions and add_residuals in making this plot.

Backward selection

```{r eval = FALSE}
birthweight %>% 
  lm(bwt ~ babysex + bhead + blength + delwt + fincome + frace + gaweeks + malform + menarche + mheight + mrace + momage +parity + pnumlbw + pnumsga +ppbmi + ppwt + smoken + wtgain, data = .) %>% 
  broom::tidy() %>% 
  knitr::kable(digits = 3)
#Eliminate frace because p>0.05 for all levels

birthweight %>% 
  lm(bwt ~ babysex + bhead + blength + delwt + fincome + gaweeks + malform + menarche + mheight + mrace + momage +parity + pnumlbw + pnumsga +ppbmi + ppwt + smoken + wtgain, data = .) %>% 
  broom::tidy() %>% 
  knitr::kable(digits = 3)
#Eliminate fincome because p>0.05

birthweight %>% 
  lm(bwt ~ babysex + bhead + blength + delwt + gaweeks + malform + menarche + mheight + mrace + momage +parity + pnumlbw + pnumsga +ppbmi + ppwt + smoken + wtgain, data = .) %>% 
  broom::tidy() %>% 
  knitr::kable(digits = 3)
#Eliminate malform1 because p>0.05

birthweight %>% 
  lm(bwt ~ babysex + bhead + blength + delwt + gaweeks + menarche + mheight + mrace + momage +parity + pnumlbw + pnumsga +ppbmi + ppwt + smoken + wtgain, data = .) %>% 
  broom::tidy() %>% 
  knitr::kable(digits = 3)
#Eliminate menarche because p>0.05

birthweight %>% 
  lm(bwt ~ babysex + bhead + blength + delwt + gaweeks + mheight + mrace + momage +parity + pnumlbw + pnumsga +ppbmi + ppwt + smoken + wtgain, data = .) %>% 
  broom::tidy() %>% 
  knitr::kable(digits = 3)
#Eliminate mheight because p>0.05

birthweight %>% 
  lm(bwt ~ babysex + bhead + blength + delwt + gaweeks + mrace + momage +parity + pnumlbw + pnumsga +ppbmi + ppwt + smoken + wtgain, data = .) %>% 
  broom::tidy() %>% 
  knitr::kable(digits = 3)
#Eliminate momage because p>0.05

birthweight %>% 
  lm(bwt ~ babysex + bhead + blength + delwt + gaweeks + mrace +parity + pnumlbw + pnumsga +ppbmi + ppwt + smoken + wtgain, data = .) %>% 
  broom::tidy() %>% 
  knitr::kable(digits = 3)
#Eliminate ppwt because p>0.05

birthweight %>% 
  lm(bwt ~ babysex + bhead + blength + delwt + gaweeks + mrace +parity + pnumlbw + pnumsga +ppbmi + smoken + wtgain, data = .) %>% 
  broom::tidy() %>% 
  knitr::kable(digits = 3)
#Eliminate wtgain because p>0.05

birthweight %>% 
  lm(bwt ~ babysex + bhead + blength + delwt + gaweeks + mrace +parity + pnumlbw + pnumsga +ppbmi + smoken, data = .) %>% 
  broom::tidy() %>% 
  knitr::kable(digits = 3)
```

Describe your modeling process and show a plot of model residuals against fitted values – use add_predictions and add_residuals in making this plot.

*I used backward selection to choose my model. I began with all variables included in the model. I then started to eliminate, one-by-one, variables that produced a p-value of >0.05. The final model that I choose is: birthweight = b0 + b1(babysex) + b2(bhead) + b3(blength) + b4(delwt) + b5(gaweeks) + b6(mrace) + b7(parity) + b8(pnumlbw) + b9(pnumsga) + b10(ppbmi) + b11(smoken). In this model, each parameter estimate produced a p-value of <0.05 which means that each estimate is statistically significant at the 5% level of significance.*

```{r warning = FALSE}
#My model is called birthweight_model
birthweight_model = birthweight %>% 
  lm(bwt ~ babysex + bhead + blength + delwt + gaweeks + mrace +parity + pnumlbw + pnumsga +ppbmi + smoken, data = .)

#Producing plot of residuals against fitted values
birthweight %>% 
  modelr::add_predictions(birthweight_model)%>%
  modelr::add_residuals(birthweight_model) %>% 
  ggplot(aes(x=pred, y = resid)) + geom_point() +
  labs (
    title = "Residuals Using Backward Selection Method",
        x = "Predictions",
        y = "Residuals"
  )
```

*The plot of residuals against fitted values shows that the residuals are centered around the 0 value. Though there are a few outliers, visually inspecting the plot, we can see that approximately half the data points fall above and half fall below 0. This is expected because we want the errors to be randomly scattered around 0. Therefore, my model is sufficient.* 


Compare your model to two others: 1) One using length at birth and gestational age as predictors (main effects only). 2) One using head circumference, length, sex, and all interactions (including the three-way interaction) between these.Make this comparison in terms of the cross-validated prediction error; use crossv_mc and functions in purrr as appropriate.

```{r}
#Preparing a training dataset.
library(modelr)
set.seed(1)
cross_valid = crossv_mc(birthweight, 100, test = 0.2) %>% 
  mutate(train = map(train, as_tibble),
         test = map(test, as_tibble))
```


```{r warning = FALSE}
#Cross-Validation: model1 is my model, model2 is the first specified model in the prompt and model3 is the second specified model in the prompt.
cross_result = cross_valid %>%  #model 1 is my model
  mutate(model1 = map(train, 
                        ~lm(bwt ~ babysex + bhead + blength + delwt + gaweeks + mrace +parity + pnumlbw + pnumsga + ppbmi + smoken, data = .x)),
         model2 = map(train, ~lm(bwt ~ blength + gaweeks, data = .x)),
         model3 = map(train, ~lm(bwt ~ bhead * blength * babysex, data = .x))) %>% 
  mutate(rmse_model1 = map2_dbl(model1, test, ~rmse(model = .x, data = .y)),
         rmse_model2 = map2_dbl(model2, test, ~rmse(model = .x, data = .y)),
         rmse_model3 = map2_dbl(model3, test, ~rmse(model = .x, data = .y)))
```


```{r}
cross_result %>% 
  dplyr::select(.id, starts_with("rmse")) %>% 
  gather(key = model, value = rmse, rmse_model1:rmse_model3) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin()
```

*According to the plot above, it appears that my model, model1 has a lower rmse compared to the two proposed models in the prompt. The second model containing the variables blength and gaweeks appears to have the highest rmse and therefore would be the least ideal model for answer the research question.*





